\myHangIndent
Oaks, J.R.
National Science Foundation Postdoctoral Research Fellowship in
Biology---Intersections of Biology and Mathematical and Physical Sciences and
Engineering.
\$207,000.
11/2013--11/2016.

\myHangIndent
Oaks, J.R.
National Research Council Postdoctoral Research Associateship---National
Institute of Standards and Technology.
\$137,200.
7/2013--7/2015.
Awarded, but declined.

\longcontent{
\myHangIndent
Oaks, J.R.
Improving methods for testing models of shared evolutionary history.
KU Office of Graduate Studies Summer Research Fellowship.
\$5,000.
5/2013--8/2013.

\myHangIndent
Oaks, J.R.
Kenneth B. Armitage Award for Excellence in Teaching.
BIOL 350---Introduction to Genetics.
\$250.
5/2011.

\ignore{
\myHangIndent
Oaks, J.R.
Comparative Phylogeography of a Dynamic Archipelago.
KU Office of Graduate Studies Summer Research Fellowship.
\$5,000.
5/2010--8/2010.
Not funded.
}

\myHangIndent
Oaks, J.R.
Comparative Phylogeography of a Dynamic Archipelago.
KU Department of Ecology and Evolutionary Biology Summer Fellowship.
\$4,000.
5/2010--8/2010.

\myHangIndent
Oaks, J.R.
Henri Seibert award for best paper in Systematics/Evolution.
\$300.
Joint Meeting of Ichthyologists and Herpetologists, Portland, Oregon, 07/09.

\myHangIndent
Oaks, J.R.
Graduate Student Enhancement.
\$15,000 (3 years).
Louisiana State University Department of Biological Sciences.
2004--2007.

\myHangIndent
Oaks, J.R.
Outstanding Biology Major Award.
\$500.
University of Wisconsin Oshkosh.
2004.

\myHangIndent
Oaks, J.R.
Leslie-Allen Fellowship in Ecology and Field Biology.
\$500.
University of Wisconsin Oshkosh.
2003.

\myHangIndent
Oaks, J.R.
Leslie-Allen Fellowship in Ecology and Field Biology.
\$500.
University of Wisconsin Oshkosh.
2002.
}

