\myHangIndent
Oaks, J.R.\ (PI).
Senior personnel: L.L.\ Grismer, C.D.\ Siler, and P.L.\ Wood, Jr.
Generalizing Bayesian Phylogenetics to Infer Shared Evolutionary Events.
National Science Foundation Division of Environmental Biology Award
\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1656004&HistoricalAwards=false}{1656004}.
5/2017--5/2021.
\$551,169.
Funded.

\myHangIndent
Armbruster, J.W.\ (PI),
J.E.\ Bond (Co-PI),
K.M.\ Halanych (Co-PI),
J.R.\ Oaks (Co-PI),
and
D. Warner (Co-PI).
CSBR: Natural History: Compactorized Shelving for the Wet Collections of the
Auburn University Museum of Natural History.
National Science Foundation Division of Biological Infrastructure Award.
1/2018--1/2020.
\$195,450.
Funded.

% \myHangIndent
% Zohdy, S.\ (PI),
% T.L.\ Goldberg (Co-PI),
% J.R.\ Oaks (Co-PI), and.
% T.\ Schwartz (Co-PI).
% The Coevolution Effect as an Ecological Driver of Viral Spillover.
% National Science Foundation Division of Environmental Biology---Ecology of Infectious Diseases.
% 7/2018--7/2020.
% \$1,996,408.
% \textbf{Not Funded}; resubmitting November 2019.

\myHangIndent
Talley, B.L.\ (PI),
J.R.\ Oaks (Co-PI),
and
M.\ Hoffman (Co-PI).
Enhancing captive breeding efforts toward the recovery of the Eastern indigo snake.
The Cooperative Endangered Species Conservation Fund (Section 6 of the
Endangered Species Act).
10/2019--10/2022.
\$190,321.20.
Funded.

\myHangIndent
Godwin, J.\ (PI),
J.J.\ Apodaca (Co-PI),
K.\ Lawson (Co-PI),
and
J.R.\ Oaks (Co-PI).
Occurrence of Western Chicken Turtle.
Louisiana Department of Wildlife and Fisheries.
10/2019--10/2022.
\$136,436.
Funded.

\myHangIndent
Zohdy, S.\ (Co-PI), T.\ Schwartz (Co-PI), J.R.\ Oaks (Co-I), and Z.\ Farris (Co-I).
The Coevolution Effect: A Mechanism for Viral Spillover into Humans.
Auburn University Intramural Grants Program.
5/2017--5/2019.
\$40,000.
Funded.

\myHangIndent
Grismer, J.L., J.R.\ Oaks, R.M.\ Brown, N.B.\ Ananjeva, X.\ Guo, and N.\
Batsaikhan.
Revisiting Przhevalsky's Expeditions: Population genetics in the Gobi Desert.
National Geographic Committee for Research and Exploration Grant.
5/2014--6/2015.
\$20,000.
Funded.

\myHangIndent
Oaks, J.R.\ (Co-PI), R.\ Brown (PI), and M.\ Holder (Co-PI).
Comparative Phylogeography of a Dynamic Archipelago.
National Science Foundation Doctoral Dissertation Improvement Grant.
8/2010--8/2012.
\$14,886.
Funded.

\longcontent{
\myHangIndent
Oaks, J.R.
Comparative Phylogeography of a Dynamic Archipelago.
KU Biodiversity Institute Panorama Grant.
5/2011--5/2012.
\$1000.
Funded.

\myHangIndent
Oaks, J.R.
Comparative Phylogeography of a Dynamic Archipelago.
KU Office of Graduate Studies Doctoral Student Research Award.
7/2011--7/2012.
\$2000.
Funded.

\ignore{
\myHangIndent
Oaks, J.R.
Comparative Phylogeography of a Dynamic Archipelago.
The Society for the Study of Evolution Rosemary Grant Graduate Research Award.
7/2010--7/2011.
\$2,085.
Not funded.
}

\myHangIndent
Oaks, J.R.
NSF stipend to attend a five-day short course, ``Comparative Methods and
Macroevolution In R.''
6/2010.
Stipend covered travel and lodging; approximately \$1,000.
Funded.

\myHangIndent
Oaks, J.R.
KU Department of Ecology and Evolutionary Biology Travel Grant.
6/2010.
\$300.
Funded.

\myHangIndent
Oaks, J.R.
KU Biodiversity Institute Travel Grant.
6/2010.
\$300.
Funded.

\myHangIndent
Oaks, J.R.
Comparative Phylogeography of Southern Indochina.
Society of Systematic Biologists Graduate Student Award.
6/2009--6/2010.
\$1650.
Funded.

\myHangIndent
Oaks, J.R.
Comparative Phylogeography of Southern Indochina.
Sigma Xi.
6/2009--6/2010.
\$1000.
Funded.

\ignore{
\myHangIndent
Oaks, J.R.
Comparative Phylogeography of Southern Indochina.
The Society for the Study of Amphibians and Reptiles Dean E. Metter Award.
6/2009--6/2010.
\$800.
Not funded.
}
\myHangIndent
Oaks, J.R.
KU Department of Ecology and Evolutionary Biology Travel Grant.
5/2010.
\$300.
Funded.

\myHangIndent
Oaks, J.R.
Estimating Species Trees Workshop Travel Grant.
University of Michigan Museum of Zoology.
1/2009.
\$500.
Funded.

\myHangIndent
Oaks, J.R.
A Six-day Course in Statistical Phylogeography.
KU Biodiversity Institute Panorama Grant.
4/2009.
\$900.
Funded.

\myHangIndent
Oaks, J.R.
A Herpetofaunal Survey and Biogeographic Study of the Cardamom Mountains in
Southeast Asia.
Louisiana State University BioGrads Grant.
5/2007--7/2007.
\$300.
Funded.

\myHangIndent
Oaks, J.R.
A Herpetofaunal Survey of Phnom Samkos, Cambodia.
Louisiana State University Museum of Natural Science Graduate Student Research
Grant.
5/2007--7/2007.
\$600.
Funded.

\myHangIndent
Oaks, J.R.
The Biogeography of the Herpetofauna of the Cardamom Mountains.
Louisiana State University BioGrads Grant.
5/2006--7/2006.
\$300.
Funded.

\myHangIndent
Oaks, J.R.
A Herpetofaunal Survey of the Cardamom Mountains, Cambodia.
Louisiana State University Museum of Natural Science Graduate Student Research
Grant.
5/2006--7/2006.
\$300.
Funded.

\myHangIndent
Oaks, J.R.
Herpetology Fieldwork in the Cardamom Mountains of Southeast Asia.
Louisiana State University BioGrads Grant.
5/2006--7/2006.
\$300.
Funded.

\myHangIndent
Oaks, J.R.
Geographic Variation of Multiple Paternity in the American alligator
(\emph{Alligator mississippiensis}): Does Selection Rescue Genetic Diversity?
Sigma Xi.
1/2005--12/2005.
\$1000.
Funded.

\myHangIndent
Oaks, J.R.
Coevolution Among Turtles and Parasites: A Test of the Tenant.
University of Wisconsin Oshkosh Undergraduate Research Grant.
6/2001--6/2002.
\$2500.
Funded.
}
