\cvitem{3em}{2024}{
    \textbf{Matt Buehler}: Henry Seibert Award
    for Best Student Oral Presentation in Evolution/Systematics
    at the Joint Meeting of Ichthyologists and Herpetologists.
}

\cvitem{3em}{2024}{
    \textbf{Matt Buehler}: Oklahoma City Zoo Conservation Action Round-up Engagement (CARE) Grant (\$5,000).
}

\cvitem{3em}{2024}{
    \textbf{Matt Buehler}: Grant from the Wildlife Foundation of Florida (\$2,000).
}

\cvitem{3em}{2024}{
    \textbf{Morgan Muell}: American Philosophical Society Lewis and Clark Award for Exploration \& Field Research (\$5,000).
}
\cvitem{3em}{2024}{
    \textbf{Morgan Muell}: Organization for Tropical Studies Henry Leigh Fellowship (\$1,631).
}
\cvitem{3em}{2024}{
    \textbf{Morgan Muell}: Organization for Tropical Studies Emily P.\ Foster Fellowship (\$1,631).
}

\cvitem{3em}{2023}{
    \textbf{Tanner Myers}: American Philosophical Society Lewis and Clark Award for Exploration \& Field Research (\$5,000).
}

\cvitem{3em}{2023}{
    \textbf{Morgan Muell}: American Society of Ichthyologists and Herpetologists Gaige Award (\$1,000).
}

\cvitem{3em}{2023}{
    \textbf{Morgan Muell}: AU COSAM Margaret McNeal Arant Memorial Award for Outstanding Achievement in Zoology (\$500).
}
\cvitem{3em}{2023}{
    \textbf{Morgan Muell}: AU DBS Nanette Chadwick Memorial Award (\$500).
}

\cvitem{3em}{2022}{
    \textbf{Claire Tracy}: Smithsonian Tropical Research Institute Fellowship (\$5,450).
}

\cvitem{3em}{2022}{
    \textbf{Tanner Myers}: Society of Systematic Biologists Graduate Student Research Award (\$2,900).
}

\cvitem{3em}{2022}{
    \textbf{Tanner Myers}: Linnean Society of London Systematics Research Award (\$500).
}

% \cvitem{3em}{2022}{
%     \textbf{Morgan Muell}: Society of Integrative and Comparative Biology Charlotte Mangum Support Award.
% }

\cvitem{3em}{2022}{
    \textbf{Morgan Muell}: Society for the Study of Reptiles and Amphibians Roger Conant Award (\$500).
}

\cvitem{3em}{2020}{
    \textbf{Randy Klabacka}: American Genetics Association Ecological,
    Evolutionary, and Conservation Genomics (EECG) Research Award (\$8,000).
}

\cvitem{3em}{2019}{
    \textbf{Kyle David}: National Science Foundation Graduate Research
    Fellowship (\$138,000).
}

\cvitem{3em}{2019}{
    \textbf{Tanner Myers}: Auburn University Presidential Graduate Research Fellowship (\$90,000).
}

\cvitem{3em}{2019}{
    \textbf{Claire Tracy}: Auburn University Presidential Graduate Research Fellowship (\$90,000).
}

\cvitem{3em}{2019}{
    \textbf{Claire Tracy}: Auburn University Allsup Fellowship (\$5,000).
}

\cvitem{3em}{2019}{
    \textbf{Randy Klabacka}: Henry Seibert Award
    for Best Student Oral Presentation in Evolution/Systematics
    at the Joint Meeting of Ichthyologists and Herpetologists.
}

\cvitem{3em}{2019}{
    % \textbf{Kyle David (advisor: Ken Halanych)}: David and Marvalee Wake Award
    \textbf{Kyle David}: David and Marvalee Wake Award
    for Best Student Oral Presentation at Annual Meeting of the Society for
    Integrative \& Comparative Biology.
    % (for presenting work that began during his rotation through my lab in
    % Spring 2018).
}

\cvitem{3em}{2018}{
    \textbf{Breanna Sipley}: National Science Foundation Graduate Research
    Fellowship (\$138,000).
}

\cvitem{3em}{2018}{
    \textbf{Nadia L'Bahy}: Awarded Best Poster Runner Up at the
    Symposium for the Auburn University Computational Biology NSF Research
    Experiences for Undergraduates.
}

\cvitem{3em}{2017}{
    \textbf{Aundrea Westfall}: Cellular and Molecular Biosciences Peaks of
    Excellence Research Fellowship (\$6,900).
}

\cvitem{3em}{2017}{
    \textbf{Breanna Sipley}: Stanley W.\ Watson Foundation Education Fund to
    attend 2017 Workshop on Molecular Evolution, Marine Biological Laboratory,
    Woods Hole, Massachusetts (\$1,502.50).
}

\cvitem{3em}{2017}{
    \textbf{Breanna Sipley}: American Society of Naturalists Travel Award to
    attend 2017 Joint Evolution meeting, Portland, Oregon (\$500).
}

\cvitem{3em}{2017}{
    \textbf{Breanna Sipley}: Society of Systematic Biologists Travel Award to
    attend TreeScaper workshop and SSB Standalone Meeting, Baton Rouge,
    Louisiana (\$500).
}

\cvitem{3em}{2017}{
    \textbf{Breanna Sipley}: Auburn University Museum of Natural History
    Meredith Ann Birchfield Endowed Fund for Excellence (\$600).
}

\cvitem{3em}{2017}{
    \textbf{Randy Klabacka}: Auburn University Museum of Natural History
    Meredith Ann Birchfield Endowed Fund for Excellence (\$1500).
}

\cvitem{3em}{2017}{
    \textbf{Randy Klabacka}: Cellular and Molecular Biosciences Peaks of
    Excellence Research Fellowship (\$6,900).
}
