\myHangIndent
Talley, B.L.\ (PI),
J.R.\ Oaks (Co-PI),
and
M.\ Hoffman (Co-PI).
Enhancing captive breeding efforts toward the recovery of the Eastern indigo snake.
The Cooperative Endangered Species Conservation Fund (Section 6 of the
Endangered Species Act).
10/2019--10/2022.
\$190,321.20.

\myHangIndent
Godwin, J.\ (PI),
J.J.\ Apodaca (Co-PI),
K.\ Lawson (Co-PI),
and
J.R.\ Oaks (Co-PI).
Occurrence of Western Chicken Turtle.
Louisiana Department of Wildlife and Fisheries.
10/2019--10/2022.
\$136,436.

\myHangIndent
Zohdy, S.\ (PI),
T.L.\ Goldberg (Co-PI),
J.R.\ Oaks (Co-PI), and.
T.\ Schwartz (Co-PI).
The Coevolution Effect as an Ecological Driver of Viral Spillover.
National Science Foundation Division of Environmental Biology---Ecology of Infectious Diseases.
7/2018--7/2020.
\$1,996,408.
Not Funded.

\myHangIndent
Armbruster, J.W.\ (PI),
J.E.\ Bond (Co-PI),
K.M.\ Halanych (Co-PI),
J.R.\ Oaks (Co-PI),
and
D. Warner (Co-PI).
CSBR: Natural History: Compactorized Shelving for the Wet Collections of the
Auburn University Museum of Natural History.
National Science Foundation Division of Biological Infrastructure Award.
1/2018--1/2020.
\$195,450.

\myHangIndent
Zohdy, S.\ (Co-PI), T.\ Schwartz (Co-PI), J.R.\ Oaks (Co-I), and Z.\ Farris (Co-I).
The Coevolution Effect: A Mechanism for Viral Spillover into Humans.
Auburn University Intramural Grants Program.
5/2017--5/2019.
\$40,000.

\myHangIndent
Oaks, J.R.\ (PI).
Senior personnel: L.L.\ Grismer, C.D.\ Siler, and P.L.\ Wood, Jr.
Generalizing Bayesian Phylogenetics to Infer Shared Evolutionary Events.
National Science Foundation Division of Environmental Biology Award
\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1656004&HistoricalAwards=false}{1656004}.
5/2017--5/2020.
\$551,169.

\myHangIndent
Oaks, J.R.\ (PI).
National Science Foundation Postdoctoral Research Fellowship in
Biology---Intersections of Biology and Mathematical and Physical Sciences and
Engineering.
11/2013--11/2016.
\$207,000.

\myHangIndent
Oaks, J.R.\ (PI).
National Research Council Postdoctoral Research Associateship---National
Institute of Standards and Technology.
7/2013--7/2015.
\$137,200.
Awarded, but declined.

\myHangIndent
Grismer, J.L.\ (Co-PI), J.R.\ Oaks (Co-PI), R.M.\ Brown (PI), N.B.\ Ananjeva
(Co-PI), X.\ Guo (Co-PI), and N.\ Batsaikhan (Co-PI).
Revisiting Prezewalski's Expeditions: Population genetics in the Gobi Desert.
National Geographic Committee for Research and Exploration Grant.
5/2014--6/2015.
\$20,000.

\myHangIndent
Oaks, J.R.\ (Co-PI), R.\ Brown (PI), and M.\ Holder (Co-PI).
Comparative Phylogeography of a Dynamic Archipelago.
National Science Foundation Doctoral Dissertation Improvement Grant.
8/2010--8/2012.
\$14,886.
